---
author: "Juan Felipe Padilla Sepúlveda"
date: "`r format(Sys.time(), '%B %Y')`"
institution: "Universidad del Valle"
division: "Social and Economic Sciences"
advisor: "Jorge Mario Uribe Gil"
department: "Economics"
degree: "Bachelor of Economics"
title: "Non-Asset-Market Uncertainty"
knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: thesisdown::thesis_pdf
abstract: |
  `r paste(readLines("00-Abstract.Rmd"), collapse = "\n  ")`
bibliography: bib/thesis.bib
link-citations: yes
colorlinks: yes
csl: csl/apa.csl
lot: true
lof: true
header-includes:
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
   - \usepackage{caption}
   - \usepackage{bm}
   - \captionsetup[figure]{font=small}
   - \captionsetup[table]{font=small}
   - \input{Notation.sty}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  fig.align = "center",
  fig.asp = 0.618,
  fig.show = "hold",
  fig.width = 6,
  out.width = "70%",
  tidy = "styler"
)

# R packages

if (!require(pacman)) install.packages("pacman")

library(pacman)

p_load(corrplot)
p_load_gh("rbagd/dynfactoR")
p_load(forcats)
p_load(ggthemes)
p_load_gh("ChandlerLutz/ggts")
p_load(here)
p_load(kableExtra)
p_load(knitr)
p_load(magrittr)
p_load(psych)
p_load(readr)
p_load(stringr)
p_load_gh("ismayc/thesisdown")
p_load(tidymodels)
p_load(tidyquant)
p_load(tidyr)
p_load(vars)
p_load(viridis)

# Global options

# Set seed of random number generator
set.seed(1112494378)

# Set theme of ggplot
theme_set(theme_tufte())

# Declare preferences
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")
conflicted::conflict_prefer("VAR", "vars")
conflicted::conflict_prefer("here", "here")
conflicted::conflict_prefer("lag", "dplyr")
```

```{bash xlsx2csv, eval = FALSE}
# Transform uncertainty indices from .xlsx to .csv

Rscript ./R/xlsx2csv.R
```

```{bash API2csv, eval = FALSE}
# Import series through FED, Yahoo Finance and Quandl API

Rscript ./R/API2csv.R
```

```{r comma}
comma <- function(x) format(x, digits = 2, big.mark = ",")
```

# Introduction {.unnumbered}

Uncertainty has been a primary concern in economics and sciences in general. Principally, since it has been separated from risk [@knight:1921]. The distinction between risk and uncertainty is that the former can be described by a distribution function with the associated probability for each possibly outcome---where each possible outcome is known---while the latter can not be characterized in this terms. This distinction between the concepts is highly important for economy that according to @bernstein:1998 it divided the history, i.e., the mastering of both phenomena mark a break in study of sciences.

Although the interpretation of uncertainty developed by Knight make him intractable in empirical studies, the current state of economics has moved to an amenable concept. That is, the time-varying conditional second moment of the series under study which is related with structural shocks such as terrorist attacks, political events, economic crises, wars and credit crunches.

From @dattetal:2017 it becomes clear that there are currently many measurements of uncertainty and each of them is used by different market agents and professionals to measure it without being sure about which one is the best. Since each one captures different movements, it is necessary to build an index following the existing ones to use as much information as possible. Henceforth, this document seeks to make three main contributions to the study of uncertainty. First, I develop a non-asset-market uncertainty index^[The monthly index is available on: <https://github.com/jpadilse/Undergraduate_Thesis/tree/master/index/Data/Output/Non-Asset-Market.csv>]---using the name of the category under which @dattetal:2017 classifies a set of uncertainty indices. This index has the ability to summarize the common comovements share in the several uncertainty indices developed so far in the literature, i.e., capture all the relevant information in the economy as a whole. Second, I analyze the dynamic relationship between uncertainty and real and financial variables in the economy. This allows us to understand the role of uncertainty inside the economy and the dynamics inside it. For instance, I document a negative relationship between uncertainty and real and financial variables. Finally, I show how the non-asset-market uncertainty index is more appealing theoretically for being less volatility---problem in newspapers-based on uncertainty measures---and had less extreme correlation with recession dates---problem in econometric measures of uncertainty. This thesis is also available as a pdf^[PDF: <https://github.com/jpadilse/Undergraduate_Thesis/blob/master/index/_book/Thesis.pdf>] and a reproducible Rmarkdown document^[Rmarkdown: <https://github.com/jpadilse/Undergraduate_Thesis>].

The rest of this document is organized as follows. First of all, I review theoretical and empirical studies of uncertainty in [Literature]. Second, I describe the methodology used to estimate the uncertainty index that is an approximate dynamic factor model in [Methodology]. Then, I present the data used and the transformations made to them in [Data]. Lastly, I show the main effects in [Results] which contains the index proposed and its relation with the United States' economy.
