---
title: "Master"
author: "Juan Felipe Padilla Sepúlveda"
date: "`r Sys.Date()`"
mainfont: Charter
fontsize: 11pt
output: 
  pdf_document:
    latex_engine: xelatex
  html_document:
    keep_md: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  fig.align = "center",
  fig.asp = 0.618,
  fig.show = "hold",
  fig.width = 6,
  out.width = "70%",
  tidy = "styler"
)

# Library calls
pacman::p_load(
  tidymodels,
  tidyquant,
  magrittr,
  tidyr,
  readr,
  stringr,
  ggthemes,
  #VIM,
  #urca,
  #quantreg,
)

# Set seed of random number generator
set.seed(1112494378)

# Set theme of ggplot
theme_set(theme_tufte())
```

# Creating a package bibliography File

```{r packages.bib}
write_bib(.packages(), file = "./packages.bib", width = 80)
```

# Preliminary

```{bash dta2csv, eval = FALSE}
# Convert the database of U.S. Call Reports from .dta to .csv

Rscript ./R/dta2csv.R
```

```{bash xlsx2csv, eval = FALSE}
# Transform uncertainty indexes from .xlsx to .csv

Rscript ./R/xlsx2csv.R
```

```{bash API2csv, eval = FALSE}
# Import series through FED, Yahoo Finance and Quandl API

Rscript ./R/API2csv.R
```

# Import databases

## U.S. Call Reports

```{r call.reports.usa}
call.reports.usa <- read_csv(
  "./Data/Input/CallReportsUSA.csv",
  col_names = c(
    "BankID",
    "Date",
    "Name",
    "TotalAssets",
    "RealStateLoans",
    "PersonalLoans",
    "AgriculturalLoans",
    "TotalEquity",
    "CILoans",
    "TotalLoans",
    "Securities",
    "TotalLiabilities"
  ),
  col_types = str_c(c("f", rep("c", 2), rep("d", 9)), collapse = ""),
  skip = 1,
  n_max = 1609540
)
```

## Uncertainty indexes

### Economic Policy Uncertainty

```{r economic.policy.uncertainty}
economic.policy.uncertainty <- read_csv(
  "./Data/Input/EPU.csv",
  col_names = c("Year", "Month", "EPU-3C", "EPU-News"),
  col_types = "?ddd",
  skip = 1,
  n_max = 417
)
```

### Monetary Policy Uncertainty

```{r monetary.policy.uncertainty.BBD}
monetary.policy.uncertainty.BBD <- read_csv(
  "./Data/Input/MPU-BBD.csv",
  col_names = c("Date", "MPU-BBD-AWN", "MPU-BBD-10"),
  col_types = "?dd",
  skip = 1,
  n_max = 393
)
```

```{r monetary.policy.uncertainty.HRS}
monetary.policy.uncertainty.HRS <- read_csv(
  "./Data/Input/MPU-HRS.csv",
  col_names = c("Date", "MPU-HRS"),
  col_types = "?d",
  skip = 1,
  n_max = 391
)
```

### Geopolitical Risk

```{r geopolitical.risk.index}
geopolitical.risk.index <- read_csv(
  "./Data/Input/GeopoliticalRiskIndex.csv",
  col_names = c("Date", "GPR", "GPT", "GPA"),
  col_types = "?ddd",
  skip = 1,
  n_max = 417
)
```

### Survey-Based Macroeconomic Uncertainty

```{r survey.based.uncertainty}
survey.based.uncertainty <- read_csv(
  "./Data/Input/SurveyBaseUncertainty.csv",
  col_names = c("Date", "SB"),
  col_types = "?d",
  skip = 1,
  n_max = 5889
)
```

### Econometric Measures of Uncertainty

```{r macro.uncertainty.JLN}
macro.uncertainty.JLN <- read_csv(
  "./Data/Input/MacroUncertaintyJLN.csv",
  col_names = c("Date", paste0("MU-JLN-h", c(1, 3, 12))),
  col_types = "?ddd",
  skip = 1,
  n_max = 702
)
```

```{r real.uncertainty.JLN}
real.uncertainty.JLN <- read_csv(
  "./Data/Input/RealUncertaintyJLN.csv",
  col_names = c("Date", paste0("RU-JLN-h", c(1, 3, 12))),
  col_types = "?ddd",
  skip = 1,
  n_max = 702
)
```

```{r financial.uncertainty.JLN}
financial.uncertainty.JLN <- read_csv(
  "./Data/Input/FinancialUncertaintyJLN.csv",
  col_names = c("Date", paste0("FU_JLN_h", c(1, 3, 12))),
  col_types = "?ddd",
  skip = 1,
  n_max = 702
)
```

## USA's raw data

```{r USA.data}
USA.data <- read_csv(
  "./Data/Input/USA-data.csv",
  col_types = str_c(c("D", rep("d", 32)), collapse = ""),
  skip = 0,
  n_max = 537
)
```

## Factors of FED data

```{r factors.FED}
factors.FED <- read_csv(
  "./Matlab/FactorsFED.csv",
  col_names = c(paste0(rep("Factor", 7), 1:7)),
  col_types = str_c(rep("d", 7), collapse = ""),
  skip = 0,
  n_max = 725
)
```

# Change format of date column

```{r Date}
# U.S. Call Reports Database
call.reports.usa %<>% mutate(Date = ymd(Date))

# Economic policy uncertainty
economic.policy.uncertainty %<>% 
  mutate(Date = seq(ymd(19850201), ymd(20191001), by = "1 month") - 1) %>% 
  select(Date, `EPU-3C`, `EPU-News`)

# Monetary policy uncertainty
monetary.policy.uncertainty.BBD %<>% 
  mutate(Date = seq(ymd(19850201), ymd(20171001), by = "1 month") - 1)

monetary.policy.uncertainty.HRS %<>% 
  mutate(Date = seq(ymd(19850201), ymd(20170801), by = "1 month") - 1)

# Geopolitical risk
geopolitical.risk.index %<>% 
  mutate(Date = seq(ymd(19850201), ymd(20191001), by = "1 month") - 1) 

# Survey-based macroeconomic uncertainty
survey.based.uncertainty %<>% mutate(Date = ymd(Date))

# Econometric measures of uncertainty
macro.uncertainty.JLN %<>%
  mutate(Date = seq(ymd(19600801), ymd(20190101), by = "1 month") - 1)

real.uncertainty.JLN %<>% 
  mutate(Date = seq(ymd(19600801), ymd(20190101), by = "1 month") - 1)

financial.uncertainty.JLN %<>% 
  mutate(Date = seq(ymd(19600801), ymd(20190101), by = "1 month") - 1)

# USA's raw data
USA.data %<>% 
  mutate(Date = seq(ymd(19750201), ymd(20190901), by = "1 month") - 1)

# Fed's data
factors.FED %<>% 
  mutate(Date = seq(ymd(19590401), ymd(20190801), by = "1 month") - 1) %>% 
  select(Date, everything())
```

# Non-Asset-Market Uncertainty Index

## Merge Indexes

```{r uncertainty.indexes}
uncertainty.indexes <- list(
  economic.policy.uncertainty,
  monetary.policy.uncertainty.BBD,
  monetary.policy.uncertainty.HRS,
  geopolitical.risk.index,
  macro.uncertainty.JLN, 
  real.uncertainty.JLN, 
  financial.uncertainty.JLN
) %>% 
  reduce(inner_join)
```

## PCA

```{r scree.plot.with.parallel.analysis}
fa.parallel(
  uncertainty.indexes[, -c(1, 2, 8, 9, 11, 12)], 
  fa = "pc", 
  n.iter = 1000, 
  show.legend = FALSE,
  main = "Scree plot with parallel analysis"
)
```

```{r principal.component}
principal.component <- principal(
  uncertainty.indexes[, -c(1, 2, 8, 9, 11, 12)], 
  nfactors = 1
)
```

## DFM

```{r dynamic.factors}
dynamic.factors <- dynfactoR::dfm(
  uncertainty.indexes[, -c(1)], 
  1, 
  1, 
  1
)

DFM.base <- tibble(
  Date = uncertainty.indexes[["Date"]],
  PCA = -dynamic.factors[["pca"]],
  QML = -dynamic.factors[["qml"]],
  TwoStep = -dynamic.factors[["twostep"]]
)
```

### Plot Non-Asset-Market Index

```{r}

```


## VAR

### Merge USA variables with uncertainty index

```{r VAR.data}
VAR.data <- USA.data %>% inner_join(DFM.base) 
```

# TEST

```{r}
# Test with JLN
VAR.data <- USA.data %>% inner_join(macro.uncertainty.JLN)

# Test with EPU
VAR.data <- USA.data %>% inner_join(monetary.policy.uncertainty.BBD)
```


# Trivariate VAR

```{r}
VAR.trivariate <- vars::VAR(
  VAR.data %>% dplyr::select(
    Production.NAICS.log.cycle, 
    Employment.manu.lin.cycle, 
    PCA
  ), 
  lag.max = 12, 
  ic = "SC"
)
```

```{r}
irf.trivariate <- vars::irf(
  VAR.trivariate, 
  impulse = "PCA", 
  response = "Production.NAICS.log.cycle",
  n.ahead = 60, 
  boot = TRUE, 
  runs = 100, 
  ci = 0.66
)

plot(irf.trivariate)
```

# Quadvariate VAR

```{r}
VAR.quadvariate <- vars::VAR(
  VAR.data %>% dplyr::select(
    Production.NAICS.log.cycle, 
    Employment.manu.lin.cycle, 
    StockMarketIndex.log.cycle,
    PCA
  ), 
  lag.max = 12, 
  ic = "SC"
)
```

```{r}
irf.quadvariate <- vars::irf(
  VAR.quadvariate, 
  impulse = "PCA", 
  response = "Production.NAICS.log.cycle",
  n.ahead = 60, 
  boot = TRUE, 
  runs = 100, 
  ci = 0.66
)

plot(irf.quadvariate)
```

# Quadvariate VAR in reverse order

```{r}
VAR.quadvariate.reverse <- vars::VAR(
  VAR.data %>% dplyr::select(
    `EPU-3C`,
    StockMarketIndex.log.cycle,
    Employment.manu.lin.cycle, 
    Production.NAICS.log.cycle 
  ), 
  lag.max = 12, 
  ic = "SC"
)
```

```{r}
irf.quadvariate.reverse <- vars::irf(
  VAR.quadvariate.reverse, 
  impulse = "EPU.3C", 
  response = "Production.NAICS.log.cycle",
  n.ahead = 60, 
  boot = TRUE, 
  runs = 100, 
  ci = 0.66
)

plot(irf.quadvariate.reverse)
```

##




```{r}
# SVAR model
# Setting up matrices for A-model
A.matrix <- matrix(NA, nrow = 11, ncol = 11)
diag(A.matrix) <- 1
A.matrix[2:11, 1]   <- 0
A.matrix[3:11, 2]   <- 0
A.matrix[4:11, 3]   <- 0
A.matrix[5:11, 4]   <- 0
A.matrix[6:11, 5]   <- 0
A.matrix[7:11, 6]   <- 0
A.matrix[8:11, 7]   <- 0
A.matrix[9:11, 8]   <- 0
A.matrix[10:11, 9]  <- 0
A.matrix[11:11, 10] <- 0

A.matrix %<>% t()

# Estimating the SVAR A-type model by direct maximization of the log-likelihood
SVAR.model <- SVAR(VAR.model, estmethod = "direct", Amat = A.matrix, hessian = TRUE)
```







# Clean U.S. Call Reports database

## Resize the database for to allow two business cycles or more for each bank

The average length of the business cycle is retrieved from NBER for the period 1945-2009: 69.5 months (trought from previous trought).

```{r business.cycles}
call.reports.usa %<>%
  semi_join(
    call.reports.usa %>%
      count(BankID) %>%
      filter(n > 47),
    by = "BankID"
  )
```

## Missing data

### Identifying missing values

```{r is.na}
sum(is.na(call.reports.usa[["CILoans"]]))

mean(is.na(call.reports.usa[["CILoans"]]))

mean(!complete.cases(call.reports.usa))
```

### Exploring missing data visually

```{r aggr}
aggr(call.reports.usa, prop = FALSE, numbers = TRUE)
```

### Delete missing values (listwise deletion) because the hardware requirements for carry on multiple imputation are too high

```{r anti_join}
call.reports.usa %<>%
  anti_join(
    call.reports.usa %>%
      filter(is.na(CILoans)) %>%
      count(BankID), 
    by = "BankID"
  )
```

# Merge the databases

```{r left_join}
call.reports.usa %<>% list(
  financial.uncertainty.JLN,
  macro.uncertainty.JLN,
  factors.FED
) %>% 
  reduce(left_join)
```

# Eliminate the individual databases

```{r rm}
rm(financial.uncertainty.JLN, macro.uncertainty.JLN, factors.FED)
```

# Growth rate

<!-- ## Replace the zeros in the commercial and industrial loans for minimum value in the sample: one unit -->

<!-- ```{r zeros.ciloans} -->
<!-- call.reports.usa %<>% mutate(CILoans = ifelse(near(CILoans, 0), 1, CILoans)) -->
<!-- ``` -->

## Experimental

```{r}
call.reports.usa %<>% 
  anti_join(
    call.reports.usa %>% 
      filter(near(CILoans, 0)) %>% 
      count(BankID),
    by = "BankID"
  )
```

## Growth rates of commercial and industrial loans for each bank

```{r growth.rate.loans}
call.reports.usa %<>%
  group_by(BankID) %>%
  mutate(
    growth.rate.ciloans = 100 * (CILoans - lag(CILoans)) / lag(CILoans),
    # growth.rate.ciloans = ifelse(
    #  is.nan(growth.rate.ciloans),
    #  0,
    #  growth.rate.ciloans
    # ),
    # growth.rate.ciloans = ifelse(
    #  near(growth.rate.ciloans, -1),
    #  -100,
    #  growth.rate.ciloans
    # ),
    growth.rate.ciloans.annualized = 4 * growth.rate.ciloans
  )
```

# Train and test split

```{r initial_split}
train.test.split <- initial_split(call.reports.usa, prop = 0.80)

call.reports.usa.train <- training(train.test.split)

call.reports.usa.test <- testing(train.test.split)
```

# Nested tibble

```{r nest}
call.reports.usa.train %<>% nest()
```

## Fit many models

```{r Macro_h1}
call.reports.usa.train %<>% mutate(
  Finan_h1 = map(
    data,
    ~rq(
      growth.rate.ciloans ~ MU_JLN_h1 + lag(MU_JLN_h1) +
        Factor1 + Factor2 + Factor3 + Factor4 + Factor5 + Factor6 + Factor7, 
      tau = 0.95, 
      data = .
    )
  )
)
```

## Model quality

```{r glance}
model.quality <- call.reports.usa.train %>% 
  mutate(Quality = map(model, glance)) %>% 
  unnest(Quality)
```

# Tidy model

```{r}
call.reports.usa.train %<>% mutate(Coeff = map(Finan_h1, tidy)) 
```

# 

```{r}
coeff <- call.reports.usa.train %>% 
  unnest(Coeff) %>% 
  filter(term == "MU_JLN_h1") %>% 
  select(estimate:tau)

coeff %>% 
  ggplot(aes(estimate)) +
    geom_histogram(bins = 180) +
    #coord_cartesian(ylim = c(0, 50)) +
    labs(
      x = quote(beta[Uncertainty]),
      y = "Count",
      title = "Distribution of the effect of macroeconomic uncertainty (h = 1)",
      caption = "Data from U.S. Call Reports, FRED-MD and Jurado et al. (2015)"
    )
ggsave("MU_JLN_h12.pdf")
```
  
# The DF-GLS test for a unit root

```{r}
call.reports.usa %>%
  filter(BankID == 37) %$%
  ur.ers(
    CILoans
  )
```

# Test one model

```{r}
SampleOne <- call.reports.usa %>% 
  filter(BankID == 37)



SampleOne %>% 
  ggplot(aes(Date, growth.rate.ciloans.annualized)) +
    geom_line()

summary(lm(growth.rate.ciloans ~ MU_JLN_h1 +
        Factor1 + Factor2 + Factor3 + Factor4 + Factor5 + Factor6 + Factor7,
  data = SampleOne))

print(rq(growth.rate.ciloans ~ MU_JLN_h1 +
        Factor1 + Factor2 + Factor3 + Factor4 + Factor5 + Factor6 + Factor7, 
   data = SampleOne))

SampleOne %>% 
  ggplot(aes(MU_JLN_h1, growth.rate.ciloans.annualized)) +
  geom_point(shape = 21) +
  geom_rangeframe() +
  stat_quantile(
    aes(colour = ..quantile..),
    quantiles = c(0.01, 0.05, 0.10, 0.25, 0.50, 0.75, 0.90, 0.95, 0.99),
    formula = y ~ x 
  ) +
  geom_smooth(method = "lm", se = FALSE, linetype = 2, colour = "red") +
  scale_colour_viridis(limits = c(0, 1)) +
  theme_tufte() +
  labs(
    x = "Diferencial de tasas de interés",
    y = "Retornos",
    colour = "Cuantiles"
  )
```


