---
title: "Report #2"
author: "Juan Felipe Padilla Sepúlveda"
date: "`r Sys.Date()`"
mainfont: Charter
fontsize: 11pt
bibliography: [References.bib, packages.bib]
csl: apa.csl
link-citations: true
output: 
  bookdown::pdf_document2:
    keep_tex: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  fig.align = "center",
  fig.asp = 0.618,
  fig.show = "hold",
  fig.width = 6,
  out.width = "70%",
  tidy = "styler"
)

# Library calls

library(dynfactoR)
library(forcats)
library(ggthemes)
library(ggts)
library(magrittr)
library(psych)
library(readr)
library(stringr)
library(tidymodels)
library(tidyquant)
library(tidyr)
library(vars)
library(viridis)

# Global options

# Set seed of random number generator
set.seed(1112494378)

# Set theme of ggplot
theme_set(theme_tufte())

# Declare preferences
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("VAR", "vars")
```

```{r write_bib, warning = FALSE}
# Creating a package bibliography File

knitr::write_bib(
  c("dynfactoR", "psych", "strucchange", "vars"), 
  file = "./packages.bib", 
  width = 80
)
```

# Raw references

## lag order

- @paultjos:1985
- @gonzpita:2002
- @kilian:2001
- @ventlutz:2005
- @kilian:1998

## fixed lag

- @leebpots:2005
- @leebpots:2006

## DFM

### Estimation

- @stocwats:2016

### Number of factors

- @baing:2002

## VAR-ref

- @stocwats:2001
- @chrieichevan:2005

## Index

- @chulguilurib:2017

## Fan chart

- @britfishwhit:1998
- @clements:2004

## Nowcasting

- @gianreicsmal:2008
- @banbruns:2011
- @banbgianreic:2011

# Data {#data}

## Source {#source}

In the empirical exercise I use uncertainty indexes from distinct sources for the USA economy. Specifically, the index are (following the non-asset-market indexes proposed in @dattlondsunbeltferriacojahaligiudroge:2017):

- The Economic Policy Uncertainty Index (EPU) developed by @bakebloodavi:2016. This Index is available from January 1985 through September 2019 in the authors website <https://www.policyuncertainty.com>. 
- The Monetary Policy Uncertainty Index (MPU) developed by @bakebloodavi:2016; henceforth BBD U.S. MPU. This Index is available from January 1985 through September 2019 in the authors website <https://www.policyuncertainty.com>. Likewise, the authors construct two variants  of them monthly MPU Index for the United States by using two different sets of newspapers.
- The Monetary Policy Uncertainty Index (MPU) developed by @hustrogesun:2019.
- The Geopolitical Risk Index developed by @caldiaco:2018.
- The macroeconomic uncertainty index developed by @juraludvng:2015.

In [Estimates on the Impact of Non--Asset-Market Uncertainty Shocks] I estimate a vector auto-regressive model. The data for this exercise were taken from the Federal Reserve Bank of Saint Louis (FRED: <https://fred.stlouisfed.org/>), Yahoo Finance (<https://finance.yahoo.com/>) and Quandl (<https://www.quandl.com/>) webpages through the API of each of them. Specifically, I use the industrial production index in 2012 prices; the total number of employees in the non-farm sector in thousand of persons; real personal consumption expenditures in 2012 prices; the personal consumption expenditures price index in 2012 prices; the average hourly earnings of production and non-supervisory employees for all-sectors in dollars per hour; average weekly hours of production and non-supervisory employees for all-sectors in hours; effective federal funds rate in percent and M2 money stock in billions of dollars from FRED. Likewise, I use the new order index from Quandl and the Standard and Poor's 500 index from Yahoo Finance. 

Also, I estimate a model for manufacturing sector in [Eight-variable VAR]. In detail, I use the industrial production index in manufacturing known as NAICS in 2012 prices, total number of employees in manufacturing in thousand of persons, average weekly hours of production and non-supervisory employees in manufacturing in hours, consumer price index (all urban consumers) in 1982-1984 prices, average hourly earnings of production and non-supervisory employees in manufacturing from FRED, and the federal funds rate and Standard and Poor's 500 index defined as above. Finally, the sample spans from January 1985 to July 2017, which is the longest period possible using these series.

## Seasonality {#seasonality}

All series were taken seasonally adjusted except the federal funds rate and the Standard and Poor's 500 index but them doesn't exhibit apparent seasonal components. Nevertheless, it is good practice to verify that the series are indeed free of seasonality [@kililutk:2017]. Therefore, I regress each series on seasonal dummies and conduct a Wald test for the inclusion of regressors. There aren't seasonality in the series. The absence of seasonal components allow to avoid the overparameterization of the VARs models.

## Transformations {#transformations}

### Basic {#basic}

All series of which units are measured in prices need to be given the $100 \times \log()$ treatment but the M2 money stock which enter as continuously compounded annual rate of change ($[(\ln(x_{t}) - \ln(x_{t - 1})) \times 100] \times 12$). 

### Detrend {#detrend}

For detrend the variables was used the alternative proposed by Hamilton [-@hamilton:2018] which avoid the shortcomings of Hodrick-Prescott (HP) filter, i.e., spurious dynamic relations that have no basis in the underlying data-generating process. The method consist of a regression of the variable at date $t + h$ on the twelve most recent values as of date $t$^[The original paper talks about quarterly data but because I use monthly data is necessary adjust the seasonally parameter to allow one year (as do the original paper with four quarters).]. The $h$ parameter is suggest to be a look-ahead period of two years which with monthly data are 24 time stamps. In summary, the model fitted to each series is an auto-regressive AR(12) model, dependent on $t + 24$ look-ahead. This is expressed more concretely by:

\begin{equation}
  y_{t+24} = \beta_{0} + \beta_{1}y_{t} + \beta_{2}y_{t - 1} + \cdots + \beta_{8}y_{t - 7} + v_{t + 24}
  (\#eq:hamilton-basic)
\end{equation}

Which can be rewritten as:

\begin{equation}
  y_{t} = \beta_{0} + \beta_{1}y_{t - 24} + \beta_{2}y_{t - 25} + \cdots + \beta_{8}y_{t - 32} + v_{t}
  (\#eq:hamilton-final)
\end{equation}

Therefore, all variables are detrended with Hamilton method in the baseline estimations.

# Results {#results}

## Non-Asset-Market Index {#non-asset-market-index}

```{r Import_Uncertainty}
source("./R/Import-Uncertainty.R")
```

```{r uncertainty_indexes, message = FALSE}
uncertainty_indexes <- list(
  economic_policy_uncertainty,
  monetary_policy_uncertainty_BBD,
  monetary_policy_uncertainty_HRS,
  geopolitical_risk_index,
  macro_uncertainty_JLN,
  real_uncertainty_JLN,
  financial_uncertainty_JLN
) %>% 
  reduce(inner_join)
```

```{r dynamic_factors, include = FALSE}
chosen_indexes <- c(
  "EPUNews", 
  "MPU_BBD_AWN", 
  "MPU_BBD_10", 
  "MPU_HRS", 
  "GPR", 
  "MU_JLN_h1"
)

dynamic_factors <- dfm(
  uncertainty_indexes %>% 
    select(!!!chosen_indexes), 
    #mutate_all(~scale(.)), 
  r = 1, 
  q = 1, 
  p = 1
)

DFM_base <- tibble(
  Date = uncertainty_indexes[["Date"]],
  PCA = dynamic_factors[["pca"]][, 1],
  TwoStep = dynamic_factors[["twostep"]][, 1],
  QML = dynamic_factors[["qml"]][, 1]
)
```

(ref:non-asset-market-index) **Non-Asset-Market-Index**: The Figure shows the non-asset-market uncertainty index from January 1985 to July 2017. Grey areas correspond to NBER recession dates (peak-to-trough), including the peaks and troughs. The horizontal line corresponds to the 95 percentile of the empirical distribution of the index. The original measure is rescaled by a factor of 100 in the plot.

```{r non-asset-market-index, cache = TRUE, fig.cap = "(ref:non-asset-market-index)"}
DFM_base %>% 
  ggplot(aes(Date, QML)) + 
    geom_cycle(fill = "grey50") +
    geom_hline(yintercept = quantile(DFM_base[["QML"]], 0.95), size = 0.125) +
    geom_line() +
    scale_x_date(date_breaks = "5 year", date_labels = "%Y") +
    labs(
      caption = "Source: Own calculations",
      x = "",
      y = ""
    )
```

```{r DescribeIndex}
DescribeIndex <- function(x) {
  skew <- skewness(x)
  kurt <- kurtosis(x) 
  AR <- lm(x ~ dplyr::lag(x))[["coefficients"]][2]
  c(skew, kurt, AR)
}
```

```{r QLR, include = FALSE}
QML_ts <- ts(DFM_base[["QML"]], start = c(1985, 1), frequency = 12)

QML_data <- ts.intersect(QML_ts, QML_ts_1 = stats::lag(QML_ts, k = -1))

QLR <- Fstats(QML_ts ~ QML_ts_1, data = QML_data)

sctest(QLR)
```

```{r date_QLR, include = FALSE}
date_QLR <- breakpoints(QML_ts ~ QML_ts_1, data = QML_data, h = 0.15)
  
coef(date_QLR, breaks = 1)
```

In Table \@ref(tab:summary-table) I report descriptive statistics for the non-asset-market uncertainty index. The skewness, kurtosis, persistence and half-life of the shocks for the full sample and for two sub-samples are presented (January 1927 to March 1940 and April 1940 to September 2014). This break date was chosen after testing for a break at an unknown date in the autoregressive model of the shocks persistence (AR(1) with drift). The basic idea is to calculate an $F$ statistic (often called Chow statistic, named for its inventor, Gregory Chow [-@chow:1960]) for each conceivable breakpoint in the interval $\tau_{0} = 0.15T$ and $\tau_{1} = 0.85T$ where $T$ is the total of observations^[That is to say, an $F$ statistic is computed for each potential breakpoint between 1989:M11 and 2012:M9, omitting the leading and trailing 15 \% of observations.], and reject the null hypothesis of structural stability if the largest of the resulting $F$ statistics exceeds a certain critical value [@andrews:2003]. This modified Chow test is variously called the *Quand Likelihood Ratio (QLR) statistic* [@quandt:1960]^[For additional discussion of estimation and testing in the presence of discrete breaks, see @hansen:2001.]. Given that there is evidence for structural change in the model is necessary dating the structural change. Bai and Perron [-@baiperr:1998;-@baiperr:2003]  established a general methodology for estimating breakpoints and their associated confidence intervals in OLS regression.

The Chow test is the Wald statistic testing
the hypothesis that the factor loadings are constant in a given equation, against the alter-
native that they have different values before and after the Great Moderation break date of
1984q4

The Quandt
likelihood ratio (QLR) version allows for an unknown break date and is the maximum
value of the Chow statistic (the sup-Wald statistic) for potential breaks in the central
70% of the sample, see Breitung and Eickmeier (2011) for additional discussion.


(ref:summary-table) **Summary Statistics of Non-Asset-Market Index**: The table reports the first-order autocorrelation coefficient and estimates of skewness and kurtosis. 

```{r summary-table, results = "asis"}
knitr::kable(
  tibble(
    Statistic = c("Skewness", "Kurtosis", "Persistence, AR(1)"),
    `1985:M1-2017:M7` = DescribeIndex(
      DFM_base[["QML"]]
    ),
    `1985:M2-2007:M7` = DescribeIndex(
      DFM_base[DFM_base[["Date"]] <= "2007-07-31", ][["QML"]]
    ),
    `2007:M8-2017:M7` = DescribeIndex(
      DFM_base[DFM_base[["Date"]] >= "2007-08-31", ][["QML"]]
    )
  )
  , digits = 2,
  , align = c("l", "c", "c", "c")
  , caption = "(ref:summary-table)"
  , caption.short = "Summary Statistics of Non-Asset-Market Index"
  , booktabs = TRUE
)
```

### PCA

```{r scree_plot_values, include = FALSE}
scree_plot <- fa.parallel(
  uncertainty_indexes %>% select(!!!chosen_indexes),
  fa = "pc",
  n.iter = 100,
  plot = FALSE
)
```

The first estimator used for construct the index is the Principal Component Estimator. Its properties are well discussed in @stocwats:2002. Because there isn't missing data the estimator is suitable.

<!-- A scree plot displays the marginal contribution of the kth principal component to the aver- -->
<!-- age R 2 of the N regressions of X t against the first k principal components. This marginal -->
<!-- contribution is the average additional explanatory value of the kth factor. When there are -->
<!-- ^ X , normalized by -->
<!-- no missing data, the scree plot is a plot of the ordered eigenvalues of sum -->
<!-- the sum of the eigenvalues. -->

Although the goal is construct one economic index from the underlying series, it is worthy show the number of components that satisfy several criteria. Each component is associated with an eigenvalue of the correlation matrix of the the raw data. The first principal component (PC) is associated with the largest eigenvalue, the second PC with the second-largest eigenvalue, and so on. The Kaiser-Harris criterion suggests retaining components with eigenvalues greater than 1 unit. Components with eigenvalues less than 1 explain less variance than contained in a single variable. In the Cattel Scree test, the eigenvalues are plotted against their component numbers. Finally, In Parallel Analysis [@haytallescar:2004] are run simulations, extracting eigenvalues from random data matrices of the same size as the original matrix of data. 

The figure \@ref(fig:scree-plot) displays the scree test based on the observed eigenvalues (as dashed line and points), the mean eigenvalues derived from 1000 random data matrices (as dotdashed line), and the eigenvalues greater than 1 (as a horizontal line at $y = 1$). Only the first PC is significantly greater than 1. Likewise, the plot shows a bend and only the PC above this sharp break is retained. Lastly, only the first PC is larger than the average corresponding eigenvalues from a set of random matrices. In summary, all three criteria suggest that a single component is appropriate for summarizing this dataset.

(ref:scree-plot) **Scree Plot**: The Figure shows a scree plot (the dashed line), eigenvalues greater than 1 criteria (solid line), and parallel analysis with 1000 simulations (dot-dashed line) suggest retaining a single component.

```{r scree-plot, cache = TRUE, dependson = c("scree_plot_values"), fig.cap = "(ref:scree-plot)"}
tibble(
  Component_Number = factor(seq_along(chosen_indexes)), 
  Real = scree_plot[["pc.values"]] / length(chosen_indexes), 
  Sim = scree_plot[["pc.sim"]] / length(chosen_indexes),
  Parallel = ifelse(Real > Sim, "greater", "less")
) %>% 
  ggplot(aes(Component_Number, Real, fill = Parallel)) +
    geom_col() +
    scale_fill_viridis_d(option = "inferno") +
    labs(
      caption = "Source: Own calculations",
      x = "Factor number (principal component number)",
      y = "Fraction of total variance of the series explained"
    ) +
    theme(legend.position = "none")
```

### Two-step 

The sconed estimator used is the Two-Step developed by @dozgianreic:2011. This methods uses PCA estimates and runs them through Kalman filter.

### QML

The third estimator used is the Quasi-Maximum Likelihood by @dozgianreic:2012. Similar to two-setp estimator, however Kalman filtering procedure is iterated until Expectation-Maximization (EM) algorithm converges.

All three estimators gives similar results, from now I use for analysis the index obtained from the Quasi-Maximum Likelihood method.

# VAR {#var}

## Estimates on the Impact of Non--Asset-Market Uncertainty Shocks {#var-baseline}

```{r Import_USA_Data, cache.extra = file.info("Import-USA-Data.R")}
source("./R/Import-USA-Data.R")
```

```{r VAR_data, message = FALSE}
VAR.data <- USA.data %>% inner_join(DFM_base) 
```

```{r}
VAR.base <- VARselect(
  VAR.data %>% select(
    Production.all.log.cycle,
    Employment.all.lin.cycle,
    Consumption.log.cycle,
    Prices.log.cycle,
    NewOrders.log.cycle,
    Wages.all.log.cycle,
    Labor.all.lin.cycle,
    FederalFundsRate.lin.cycle,
    StockMarketIndex.log.cycle,
    M2.cca.cycle,
    PCA
  ),
  lag.max = 24
)
```


```{r VAR_baseline}
VAR.baseline <- VAR(
  VAR.data %>% select(
    Production.all.log.cycle,
    Employment.all.lin.cycle,
    Consumption.log.cycle,
    Prices.log.cycle,
    NewOrders.log.cycle,
    Wages.all.log.cycle,
    Labor.all.lin.cycle,
    FederalFundsRate.lin.cycle,
    StockMarketIndex.log.cycle,
    M2.cca.cycle,
    PCA
  ),
  lag.max = 12,
  ic = "SC"
)
```

```{r irf_baseline, warning = FALSE}
irf.baseline <- irf(
  VAR.baseline, 
  impulse = "PCA", 
  n.ahead = 60, 
  runs = 100, 
  ci = 0.86
)
```

```{r irf_baseline_matrix}
matrix.response <- as_tibble(irf.baseline[["irf"]][["PCA"]]) %>% 
  mutate(Months = row_number()) %>% 
  pivot_longer(-Months, names_to = "Variable", values_to = "Response")

matrix.lower <- as_tibble(irf.baseline[["Lower"]][["PCA"]]) %>% 
  mutate(Months = row_number()) %>%
  pivot_longer(-Months, names_to = "Variable", values_to = "Lower")

matrix.upper <- as_tibble(irf.baseline[["Upper"]][["PCA"]]) %>% 
  mutate(Months = row_number()) %>%
  pivot_longer(-Months, names_to = "Variable", values_to = "Upper")

matrix.irf <- list(matrix.response, matrix.lower, matrix.upper) %>% 
  reduce(inner_join, by  = c("Variable", "Months")) %>% 
  select(Variable, Months, Response, Lower, Upper) %>% 
  arrange(Variable, Months) %>% 
  mutate(
    Variable = factor(Variable),
    Variable = fct_recode(
      Variable,
      "Production" = "Production.all.log.cycle",
      "Employment" = "Employment.all.lin.cycle",
      "New Orders" = "NewOrders.log.cycle",
      "Consumption" = "Consumption.log.cycle",
      "Federal Funds Rate" = "FederalFundsRate.lin.cycle",
      "Stock Market Index" = "StockMarketIndex.log.cycle"
    )
  )
```

(ref:irf-baseline-plot) **Economic Dynamics under Uncertainty**: The Figure shows the reaction of the variables to an unexpected increment of non-asset-market uncertainty, based on 1000 replications. The estimation period runs from January 1985 to July 2017. The axes are in percentages but the federal funds rate and employment are in basic points. Confidence bands (86 \%) are calculated using bootstrapping techniques as explained in @efrotibs:1993.

```{r irf-baseline-plot, cache = TRUE, dependson = c("irf_baseline_matrix", "irf_baseline", "VAR_baseline", "VAR_data", "Import_USA_Data"), fig.asp = 1.236, fig.cap = "(ref:irf-baseline-plot)"}
matrix.irf %>% 
  filter(Variable %in% c(
    "Production",
    "Employment",
    "New Orders",
    "Consumption",
    "Federal Funds Rate",
    "Stock Market Index"
  )) %>% 
  ggplot(aes(Months, Response)) +
    geom_hline(aes(yintercept = 0), size = 0.125) +
    geom_ribbon(aes(ymin = Lower, ymax = Upper), fill = "steelblue", alpha = 0.125) +
    geom_line(colour = "steelblue", linetype = "dashed") +
    scale_x_continuous(breaks = seq(0, 60, by = 10)) + 
    facet_wrap(
      ~ Variable, 
      nrow = 3,
      scales = "free_y", 
    ) +
    labs(
      caption = "Source: Own calculations",
      x = "Months after the shock",
      y = "Impact"
    )
```

```{r Granger}
Granger <- function(Cause) {
  causality(VAR.baseline, cause = Cause)[["Granger"]][["p.value"]]
}
```

```{r}
Names_VAR <-   c(
  "Production",
  "Employment",
  "Consumption",
  "Prices",
  "New Orders",
  "Wages",
  "Labor",
  "Federal Funds rate",
  "Stock market index",
  "M2",
  "Uncertainty"
)

p_values_granger <- map_dbl(
  list(
    "Production.all.log.cycle",
    "Employment.all.lin.cycle",
    "Consumption.log.cycle",
    "Prices.log.cycle",
    "NewOrders.log.cycle",
    "Wages.all.log.cycle",
    "Labor.all.lin.cycle",
    "FederalFundsRate.lin.cycle",
    "StockMarketIndex.log.cycle",
    "M2.cca.cycle",
    "PCA"
  )
  , Granger
)
```

(ref:Granger-table) **Granger-Causality Tests**: The entries show the $p$-values for F-tests that lags of the variable in the row labeled Regressor do not enter the reduced form equation for all remaining variables.

```{r Granger-table, results = "asis"}
knitr::kable(
  tibble(
    Regressor = Names_VAR,
    `p-values` = p_values_granger
  )
  , digits = 2,
  , align = c("l", "c"),
  , caption = "(ref:Granger-table)"
  , caption.short = "Granger-Causality Tests",
  , booktabs = TRUE
  , linesep = ""
)
```

## Robustness {#robustness}

### Eight-variable VAR {#var-eight}

```{r var_medium_lag}
VAR_medium_lag <- VARselect(
  VAR.data %>% select(
    Production.NAICS.log.cycle, 
    Employment.manu.lin.cycle, 
    Labor.manu.lin.cycle,
    Prices.urban.log.cycle,
    Wages.manu.log.cycle,
    FederalFundsRate.lin.cycle,
    StockMarketIndex.log.cycle,
    PCA
  ), 
  lag.max = 12
)
```

```{r VAR_medium}
VAR_medium <- VAR(
  VAR.data %>% select(
    Production.NAICS.log.cycle, 
    Employment.manu.lin.cycle, 
    Labor.manu.lin.cycle,
    Prices.urban.log.cycle,
    Wages.manu.log.cycle,
    FederalFundsRate.lin.cycle,
    StockMarketIndex.log.cycle,
    PCA
  ), 
  lag.max = 12, 
  ic = "AIC"
)
```

```{r irf_medium_production, warning = FALSE}
irf_medium_production <- irf(
  VAR_medium, 
  impulse = c("PCA", "StockMarketIndex.log.cycle"), 
  response = "Production.NAICS.log.cycle",
  n.ahead = 60, 
  runs = 100, 
  ci = 0.68
)
```

```{r irf_medium_production_matrix}
data_plot <- tibble(
  Months = 0:60,
  `Response to a uncertainty shock` = as.vector(
    irf_medium_production[["irf"]][["PCA"]]
  ),
  PCA_lower = as.vector(irf_medium_production[["Lower"]][["PCA"]]),
  PCA_upper = as.vector(irf_medium_production[["Upper"]][["PCA"]]),
  `Response to a stock market shock` = -as.vector(
    irf_medium_production[["irf"]][["StockMarketIndex.log.cycle"]]
  )
) %>% 
  gather(
    `Response to a uncertainty shock`, 
    `Response to a stock market shock`, 
    key = "Imp", 
    value = "Res"
  )
```

(ref:production-medium) **Decline of production under uncertainty**: The Figure shows the reaction of industrial production in manufacturing to an unexpected increment of non--asset-market uncertainty and to an unexpected fall the stock-market (model with 3 lags, selected by the Akaike Information Criterion), based on 1000 replications. The estimation period runs from January 1985 to July 2017. The axe is in percentage. Confidence bands (86 \%) are calculated using bootstrapping techniques as explained in @efrotibs:1993.

```{r production-medium, cache = TRUE, fig.cap = "(ref:production-medium)"}
data_plot %>% 
  ggplot(aes(Months, Res)) +
    geom_hline(aes(yintercept = 0), size = 0.125) +
    geom_ribbon(
      data = data_plot %>% filter(Imp == "Response to a uncertainty shock"), 
      aes(ymin = PCA_lower, ymax = PCA_upper), 
      fill = "steelblue", 
      alpha = 0.125
    ) +
    geom_line(aes(colour = Imp, linetype = Imp)) +
    scale_x_continuous(breaks = seq(0, 60, by = 5)) +
    scale_y_continuous(breaks = seq(0.20, -0.60, by = -0.05)) +
    scale_color_manual(values = c(viridis(1), "steelblue")) +
    scale_linetype_manual(values = c("dotdash", "dashed")) +
    labs(
      caption = "Source: Own calculations",
      x = "Months after the shock",
      y = "% impact on production",
      colour = "",
      linetype = ""
    ) +
    theme(legend.position = "bottom")
```

```{r irf_medium_employment, warning = FALSE}
irf_medium_employment <- irf(
  VAR_medium, 
  impulse = c("PCA", "StockMarketIndex.log.cycle"), 
  response = "Employment.manu.lin.cycle",
  n.ahead = 60, 
  runs = 100, 
  ci = 0.68
)
```

```{r irf_medium_employment_matrix}
data_plot <- tibble(
  Months = 0:60,
  `Response to a uncertainty shock` = as.vector(
    irf_medium_employment[["irf"]][["PCA"]]
  ),
  PCA_lower = as.vector(irf_medium_employment[["Lower"]][["PCA"]]),
  PCA_upper = as.vector(irf_medium_employment[["Upper"]][["PCA"]]),
  `Response to a stock market shock` = -as.vector(
    irf_medium_employment[["irf"]][["StockMarketIndex.log.cycle"]]
  )
) %>% 
  gather(
    `Response to a uncertainty shock`, 
    `Response to a stock market shock`, 
    key = "Imp", 
    value = "Res"
  )
```

(ref:employment-medium) **Decline of employment under uncertainty**: The Figure shows the reaction of employment in manufacturing to an unexpected increment of non-asset-market uncertainty and to an unexpected fall the stock-market, based on 1000 replications. The estimation period runs from January 1985 to July 2017. The axe is in percentage. Confidence bands (86 \%) are calculated using bootstrapping techniques as explained in @efrotibs:1993.

```{r employment-medium, cache = TRUE, fig.cap = "(ref:employment-medium)"}
data_plot %>% 
  ggplot(aes(Months, Res)) +
    geom_hline(aes(yintercept = 0), size = 0.125) +
    geom_ribbon(
      data = data_plot %>% filter(Imp == "Response to a uncertainty shock"), 
      aes(ymin = PCA_lower, ymax = PCA_upper), 
      fill = "steelblue", 
      alpha = 0.125
    ) +
    geom_line(aes(colour = Imp, linetype = Imp)) +
    scale_x_continuous(breaks = seq(0, 60, by = 5)) +
    scale_y_continuous(breaks = seq(20, -60, by = -10)) +
    scale_color_manual(values = c(viridis(1), "steelblue")) +
    scale_linetype_manual(values = c("dotdash", "dashed")) +
    labs(
      caption = "Source: Own calculations",
      x = "Months after the shock",
      y = "Impact on employment",
      colour = "",
      linetype = ""
    ) +
    theme(legend.position = "bottom")
```

The set the variables in the estimation are industrial production in manufacturing, employment in manufacturing, average hours in manufacturing, consumer price index, average hourly earnings for production workers in manufacturing, federal funds rate, stock-market index and non-asset-market uncertainty.

To identify uncertainty shocks, a Cholesky ordering is used with production ordered first, followed by employment, labor, prices, wages, federal funds rate, stock market index and non-market uncertainty ordered last. The ordering is based on the assumptions that shocks instantaneously influence the stock market, then prices (wages, the consumer price index (CPI), and interest rates), and finally quantities (hours, employment, and output).

Figure \@ref(fig:production-medium) plots the impulse response function of industrial production (the dashed line) to a non-market uncertainty shock. Industrial production displays a fall of around 0.30 \% within 12 months. The confidence bands (shaded area) are plotted around this, highlighting that this drop is statistically significant. For comparison to a first-moment shock, the response to a fall the stock-market is also plotted (dotted line) displaying a much more large drop over the subsequent 2 years. Figure \@ref(fig:employment-medium) repeats the same exercise for employment, displaying a similar drop in activity.

```{r fevd_medium, warning = FALSE}
fevd_medium <- fevd(VAR_medium, 60)
```

```{r fevd_medium_production}
fevd_medium_production <- as_tibble(
  fevd_medium[["Production.NAICS.log.cycle"]]
)

fevd_medium_production %<>% 
  rename(
    Production = Production.NAICS.log.cycle,
    Employment = Employment.manu.lin.cycle,
    Prices = Prices.urban.log.cycle,
    Wages = Wages.manu.log.cycle,
    Labor = Labor.manu.lin.cycle,
    `Federal funds rate` = FederalFundsRate.lin.cycle,
    `Stock market index` = StockMarketIndex.log.cycle,
    Uncertainty = PCA  
  ) %>% 
  mutate(N = row_number()) %>% 
  gather(Production:Uncertainty, key = "Variable", value = "Percentage") %>% 
  mutate(Variable = factor(Variable, levels = unique(Variable))) %>% 
  arrange(N)
```

```{r fevd_medium_R}
fevd_medium_R <- as_tibble(
  fevd_medium[["FederalFundsRate.lin.cycle"]]
)

fevd_medium_R %<>% 
  rename(
    Production = Production.NAICS.log.cycle,
    Employment = Employment.manu.lin.cycle,
    Prices = Prices.urban.log.cycle,
    Wages = Wages.manu.log.cycle,
    Labor = Labor.manu.lin.cycle,
    `Federal funds rate` = FederalFundsRate.lin.cycle,
    `Stock market index` = StockMarketIndex.log.cycle,
    Uncertainty = PCA  
  ) %>% 
  mutate(N = row_number()) %>% 
  gather(Production:Uncertainty, key = "Variable", value = "Percentage") %>% 
  mutate(Variable = factor(Variable, levels = unique(Variable))) %>%
  arrange(N) 
```

(ref:fevd-medium-production) **Forecast error variance decomposition for production**: The Figure shows fractions of the forecast error variance due to production shocks for the eight variables. The sample period is January 1985 to July 2017.

```{r fevd-medium-production-plot, cache = TRUE, fig.cap = "(ref:fevd-medium-production)"}
fevd_medium_production %>% 
  ggplot(aes(N, Percentage)) +
    geom_area(aes(fill = Variable), colour = "black", size = 0.20) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.10), labels = percent) +
    scale_x_continuous(breaks = c(1, 6, 12, 18, 24, 30, 36, 42, 48, 54, 60)) +
    scale_fill_viridis_d(option = "inferno") +
    labs(
    caption = "Source: Own calculations",
    x = "Horizont",
    y = "",
    fill = ""
    )
```

(ref:fevd-medium-R-plot) **Forecast error variance decomposition for federal funds rate**: The Figure shows fractions of the forecast error variance due to federal funds rate shocks for the eight variables. The sample period is January 1985 to July 2017.

```{r fevd-medium-R-plot, cache = TRUE, fig.cap = "(ref:fevd-medium-R-plot)"}
fevd_medium_R %>% 
  ggplot(aes(N, Percentage)) +
    geom_area(aes(fill = Variable), colour = "black", size = 0.20) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.10), labels = percent) +
    scale_x_continuous(breaks = c(1, 6, 12, 18, 24, 30, 36, 42, 48, 54, 60)) +
    scale_fill_viridis_d(option = "inferno") +
    labs(
    caption = "Source: Own calculations",
    x = "Horizont",
    y = "",
    fill = ""
    )
```


### Alternative sets and orderings of variables {#sets-order}

```{r VAR_trivariate}
VAR.trivariate <- VAR(
  VAR.data %>% select(
    Production.NAICS.log.cycle, 
    Employment.manu.lin.cycle, 
    PCA
  ), 
  lag.max = 12, 
  ic = "SC"
)
```

```{r irf_trivariate, warning = FALSE}
irf.trivariate <- irf(
  VAR.trivariate, 
  impulse = "PCA", 
  response = "Production.NAICS.log.cycle",
  n.ahead = 60, 
  runs = 100, 
  ci = 0.86
)
```

```{r VAR_quadvariate}
VAR.quadvariate <- VAR(
  VAR.data %>% select(
    Production.NAICS.log.cycle, 
    Employment.manu.lin.cycle, 
    StockMarketIndex.log.cycle,
    PCA
  ), 
  lag.max = 12, 
  ic = "SC"
)
```

```{r irf_quadvariate, warning = FALSE}
irf.quadvariate <- irf(
  VAR.quadvariate, 
  impulse = "PCA", 
  response = "Production.NAICS.log.cycle",
  n.ahead = 60, 
  runs = 100, 
  ci = 0.86
)
```

```{r VAR_quadvariate_reverse}
VAR.quadvariate.reverse <- VAR(
  VAR.data %>% select(
    PCA,
    StockMarketIndex.log.cycle,
    Employment.manu.lin.cycle, 
    Production.NAICS.log.cycle 
  ), 
  lag.max = 12, 
  ic = "SC"
)
```

```{r irf_quadvariate_reverse, warning = FALSE}
irf.quadvariate.reverse <- irf(
  VAR.quadvariate.reverse, 
  impulse = "PCA", 
  response = "Production.NAICS.log.cycle",
  n.ahead = 60, 
  runs = 100, 
  ci = 0.86
)
```

In Figure \@ref(fig:robustness) the VAR is reestimated using a simple trivariate VAR (industrial production, employment and non-asset-market uncertainty index only) also display a drop (dashed line). The "quadvariate" VAR (industrial production, employment, stock-market and non-asset-market uncertainty index only) also displays a similar drop (solid line), as does the quadvariate VAR with the variable ordering reversed (dotted line). Hence the response of industrial production to a uncertainty shock appears robust to both the basic selection and the ordering of variables.

(ref:robustness) **VAR model is robust to different variable sets and ordering**: The Figure shows the reaction of the industrial production to an unexpected increment of non-asset-market uncertainty. The estimation period runs from January 1985 to July 2017. The axe is in percentage. The models are defined as: trivariate (industrial production, employment and non-asset-market uncertainty shocks), Quadvariate (industrial production, employment, stock-market and non-asset-market uncertainty shocks) and Quadvariate in reverse (non-asset-market uncertainty shocks, stock-market, employment and industrial production).

```{r robustness, cache = TRUE, fig.cap = "(ref:robustness)"}
tibble(
  Months = 0:60,
  Trivariate = irf.trivariate[["irf"]][["PCA"]],
  Quadvariate = irf.quadvariate[["irf"]][["PCA"]],
  `Quadvariate in reverse` = irf.quadvariate.reverse[["irf"]][["PCA"]]
) %>% 
  gather(
    Trivariate, Quadvariate, `Quadvariate in reverse`, 
    key = "VAR", 
    value = "Shock"
  ) %>% 
  ggplot(aes(Months, Shock)) +
    geom_hline(aes(yintercept = 0), size = 0.125) +
    geom_line(aes(colour = VAR, linetype = VAR)) +
    scale_x_continuous(breaks = seq(0, 60, by = 5)) +
    scale_y_continuous(breaks = seq(0, -0.40, by = -0.05)) +
    scale_color_viridis_d() +
    labs(
      caption = "Source: Own calculations",
      x = "Months after the shock",
      y = "% impact on production",
      colour = "",
      linetype = ""
    ) +
    theme(legend.position = "bottom")
```

# Forecasting

```{r EndOfSample}
# End of sample dates
EndOfSample <- VAR.data %>% 
  tail(nrow(.) - quantile(1:nrow(.), 0.90) + 1) %>% 
  pull(Date) 
```

```{r forecast_horizont}
forecast_horizont <- list(3, 6, 9)
```

```{r RMSFE_VAR}
RMSFE_VAR <- function(end_date, number_ahead) {
  # Variables chosen
  VAR_data_RMSFE <- c(
    "Production.NAICS.log.cycle", 
    "Employment.manu.lin.cycle", 
    "Labor.manu.lin.cycle",
    "Prices.urban.log.cycle",
    "Wages.manu.log.cycle",
    "FederalFundsRate.lin.cycle",
    "StockMarketIndex.log.cycle",
    "PCA"
  )
  
  # Estimate VAR model
  VAR_model <- VAR(
    VAR.data %>% 
      filter(Date <= end_date) %>% 
      select(VAR_data_RMSFE),
    lag.max = 24, 
    ic = "AIC"
  )
  
  # Sample data for n-period ahead forecast
  raw_data <- VAR.data %>% 
    filter(
      between(
        Date,
        ceiling_date(end_date %m+% months(1), unit = "month") - days(1),
        ceiling_date(end_date %m+% months(number_ahead), unit = "month") - days(1)
      )
    ) %>% 
    select(VAR_data_RMSFE)
  
  # Compute forecast
  raw_predictions <- bind_rows(
    predict(VAR_model, n.ahead = number_ahead)[["fcst"]], 
    .id = "column_label"
  ) %>% 
    head(number_ahead) %>% 
    select(-column_label)
  
  # Compute pseudo-out-of-sample forecast errors
  raw_data - raw_predictions
}
```

```{r Forecast_error}
Forecast_error <- function(n_ahead) {
  FE <- map_dfr(
    EndOfSample %>% head(-n_ahead),
    RMSFE_VAR,
    number_ahead = n_ahead
  ) %>% 
  summarise_all(~sqrt(mean(.)^2)) 
  
  FE
}
```

```{r Forecast_error_data, warning = FALSE}
Forecast_error_data <- map_dfr(forecast_horizont, Forecast_error)
```

```{r RMSFE-non-asset-market, results = "asis"}
knitr::kable(
  Forecast_error_data
  , digits = 2,
  , align = c("l", rep("c", 8))
  , caption = "(ref:RMSFE-non-asset-market)"
  , caption.short = "Root Mean Squared Errors of Simulated Out-Of-Sample Forecasts"
  , booktabs = TRUE
)
```


\clearpage

# Appendix {-}

In the estimations I make use of the r-package `dynfactoR` [@R-dynfactoR] to estimate the DFM, the r-package `psych` [@R-psych] to select the optimal number of components, to estimate structural breaks in the index I employ the r-package `strucchange` [@R-strucchange] and to estimate the VARs models the r-package `vars` [@R-vars] was used.

\clearpage

# References
